Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2016-02-14 3dpas_intro.tex
more refinement.

This section brings together some key observations from the applications and
infrastructure analysis carried out in this paper.  Section~\ref{sec:discussion}
provides a discussion of dynamic and distributed characteristics of data
associated with the applications we analyze in this work, attempting to infer
more general characteristics that %can be applied
may apply to other similar applications.  We also suggest two metrics that may
suggest two metrics that may be associated with such applications, primarily as
a basis to compare how compute and data processing (in terms of their number and
distribution) may be used to find common features between them. Such feature
analysis is useful, we believe, for two main reasons: (i) to identify
similarities between the applications covered in \S\ref{sec:scenarios} with
others that are in the design phase or under development, so that common
requirements can be identified; and (ii) to identify gaps in current software
tools and programming systems that such applications use, thereby leading to the
development of new tools and systems. As our application and infrastructure
coverage is, by necessity, limited, identifying common features also enables the
lessons learned to be generalized and applied more widely. We subsequently
discuss a set of architectures for D3 science, and pose some questions we
believe are pertinent as the community begins considering the next-generation
architectures for D3 applications. In \S\ref{sec:conclusion} we conclude by
providing a number of observations to inform applications and
cyberinfrastructure developers, based on common trends found in our study.

An important motivation for this work is to capture the state of the
art in the design and development of distributed dynamic applications
and the associated infrastructure currently used for their
execution. We have aimed to try to discern common
approaches and challenges, and to identify any obvious gaps (or
opportunities). Using a common vocabulary and terminology
to describe otherwise distinct and unrelated applications allows
potential application
users/developers to benefit from the insight that a common
analytical framework provides. For example, seeing how
applications with similar patterns (e.g., pipelines) have addressed
issues of dynamism and distribution enables common solutions and
facilitates the emergence of best practices even in the absence of formal
methods.  Similarly, our analysis sends a useful message to domain and
application scientists that the challenges and barriers they face are not
unique even if current solutions require a level of customization.

@@

Associated with the growth in data volumes are increasing levels of dynamism and
distribution; sometimes distribution is logical, but sometimes the data is
physically distributed for reasons of performance or convenience. At large
scales, dynamism becomes intrinsic to the application and infrastructure;
sometimes it occurs because of changing experimental or analytic conditions,
sometimes due to the availability of infrastructure and resources. In this
paper, we have identified many different applications characteristics,
programming systems, and infrastructure techniques that either support dynamic
data or produce it.

>>>>

This section brings together some key observations from the analysis of
applications and infrastructure carried out in this paper.
Section~\ref{sec:discussion} provides a discussion of dynamic and distributed
characteristics of data associated with a set of applications.

% we analyze in this work, attempting to infer more general characteristics
% that %can be applied
% may apply to other similar applications.
%suggest two metrics that may

We suggest two metrics that may be associated with such applications, primarily
as a basis to compare how compute and data processing (in terms of their number
and distribution) may be used to find common features between them. Such feature
analysis is useful, we believe, for two main reasons: (i) to identify
similarities between the applications covered in \S\ref{sec:scenarios} with
others that are in the design phase or under development, so that common
requirements can be identified; and (ii) to identify gaps in current software
tools and programming systems that such applications use, thereby leading to the
development of new tools and systems.

As our application and infrastructure coverage is, by necessity, limited,
identifying common features also enables the lessons learned to be generalized
and applied more widely. We subsequently discuss a set of architectures for D3
science, and pose some questions we believe are pertinent as the community
begins considering the next-generation architectures for D3 applications. In
\S\ref{sec:conclusion} we conclude by providing a number of observations to
inform applications and cyberinfrastructure developers, based on common trends
found in our study.

@@

Associated with the growth in data volumes are increasing levels of dynamism and
distribution; sometimes distribution is logical, but sometimes the data is
physically distributed for reasons of performance or convenience. At large
scales, dynamism becomes intrinsic to the application and infrastructure;
sometimes it occurs because of changing experimental or analytic conditions,
sometimes due to the availability of infrastructure and resources.

An important motivation for this work is to capture the state of the art in the
design and development of distributed dynamic applications and the associated
infrastructure currently used for their execution. We have aimed to try to
discern common approaches and challenges, and to identify any obvious gaps (or
opportunities). Using a common vocabulary and terminology to describe otherwise
distinct and unrelated applications allows potential application
users/developers to benefit from the insight that a common analytical framework
provides. For example, seeing how applications with similar patterns (e.g.,
pipelines) have addressed issues of dynamism and distribution enables common
solutions and facilitates the emergence of best practices even in the absence of
formal methods.  Similarly, our analysis sends a useful message to domain and
application scientists that the challenges and barriers they face are not unique
even if current solutions require a level of customization.  In this paper, we
have identified many different applications characteristics, programming
systems, and infrastructure techniques that either support dynamic data or
produce it.
